Twists of supersymmetric gauge theories

### 2020-01-13 paper.tex

>>>>

\begin{table}[!h]
 \centering
 \begin{tabular}{c|c|c|c|c}
 $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{2}*{10} & \multirow{2}*{$(1,0)$} & \multirow{2}*{Rank $(1,0)$} & Holomorphic Chern-Simons Theory & \multirow{2}*{5 (holomorphic)} \\
 &&&$\bun_G(\CC^5)$ &\\ \hline
 \multirow{2}*{9} & \multirow{2}*{1} & \multirow{2}*{Rank 1} & Mixed Chern-Simons Theory & \multirow{2}*{5 (minimal)} \\
 &&&$\bun_G(\CC^4 \times \RR_{\mr{dR}})$ &\\ \hline
 \multirow{6}*{8} & \multirow{6}*{1} & \multirow{2}*{Rank $(1,0)$ Pure} & Holomorphic BF Theory & \multirow{2}*{4 (holomorphic)} \\
 &&& $T^*_{\mr{odd}}\bun_G(\CC^4, BG)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(1,1)$} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
 &&& $\bun_G(\CC^3 \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
  && \multirow{2}*{Rank $(1,0)$ Impure} & Perturbatively trivial ($\Spin(7)$ Instanton)& \multirow{2}*{8 (topological)} \\
 &&& $\bun_G(\CC^4, BG)_\mr{dR}$ & \\ \hline
  \multirow{6}*{7} & \multirow{6}*{1} & \multirow{2}*{Rank $1$ Pure} & Mixed BF Theory & \multirow{2}*{4 (minimal)} \\
 &&& $T^*[-1]\bun_G(\CC^3 \times \RR_{\mr{dR}}, BG)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
 &&& $\bun_G(\CC^2 \times \RR^3_{\mr{dR}})$ & \\ \cline{3-5}
  && \multirow{2}*{Rank $1$ Impure} & Perturbatively trivial ($G_2$ Monopole)& \multirow{2}*{7 (topological)} \\
 &&& $\bun_G(\CC^3 \times \RR_{\mr{dR}}, BG)_\mr{dR}$ & \\ \hline
 \multirow{8}*{6} & \multirow{8}*{$(1,1)$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{3 (holomorphic)} \\
 &&& $T^*[-1]\mr{Map}(\CC^3, \gg/\gg)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(1,1)$ special} & {Mixed BF Theory} & \multirow{2}*{4} \\
 &&& $T^*[-1]\bun_G(\CC^2 \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(2,2)$} & {Mixed Chern-Simons Theory} & \multirow{2}*{5} \\
 &&& $\bun_G(\CC \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(1,1)$ generic} & {Perturbatively trivial (6d Hitchin system)} & \multirow{2}*{6 (topological)} \\
 &&& $\bun_G(\CC^2 \times \RR^2_{\mr{dR}})_{\mr{dR}}$ & \\ \hline
 \multirow{8}*{5} & \multirow{8}*{$2$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory} & \multirow{2}*{3 (minimal)} \\
 &&& $T^*[-1]\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, \gg/\gg)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ special} & {Mixed BF Theory} & \multirow{2}*{4} \\
 &&& $T^*[-1]\bun_G(\CC \times \RR^3_{\mr{dR}})$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $4$} & {5d Chern-Simons Theory} & \multirow{2}*{5 (topological)} \\
 &&& $\bun_G(\RR^5_{\mr{dR}})$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ generic} & {Perturbatively trivial (Haydys-Witten)} & \multirow{2}*{5 (topological)} \\
 &&& $\bun_G(\CC \times \RR^3_{\mr{dR}})_{\mr{dR}}$ & \\ \hline
 \multirow{10}*{4} & \multirow{10}*{$4$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
 &&& $T^*[-1]\higgs_G(\CC^2)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(1,1)$} & Mixed BF Theory & \multirow{2}*{3} \\
 &&& $T^*[-1]\bun_G(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(2,2)$ special} & BF Theory (Kapustin-Witten B-model) & \multirow{2}*{4 (topological)} \\
 &&& $T^*[-1]\flat_G(\RR^4)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(2,1)$} & {Perturbatively trivial} & \multirow{2}*{4 (topological)} \\
 &&& $\bun_G(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}})_{\mr{dR}}$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Kapustin-Witten A-Model)} & \multirow{2}*{4 (topological)} \\
 &&& $\higgs_G(\CC^2)_{\mr{dR}}$ & \\ \hline
  \multirow{6}*{3} & \multirow{6}*{$8$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory} & \multirow{2}*{2 (minimal)} \\
 &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, T^*[2](\gg/\gg))$  & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ (B)} & {BF Theory (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, T^*[2](\gg/\gg))$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
 %\multirow{6}*{2} & \multirow{6}*{$(8,8)$} & \multirow{2}*{Rank $(1,0)$} & {} & \multirow{2}*{1 (holomorphic)} \\
 %&&& {} & \\ \cline{3-5}
 %&& \multirow{2}*{Rank $(1,1)$ (B)} & {} & \multirow{2}*{2 (topological)} \\
 %&&& {} & \\ \cline{3-5}
 %&& \multirow{2}*{Rank $(1,1)$ (A)} & {} & \multirow{2}*{2 (topological)} \\
 %&&& {} & \\ \hline
 \end{tabular}
 \caption{Twists of Maximally Supersymmetric Pure Yang-Mills Theories with gauge group $G$ (16 supercharges).}
 \label{table_of_twists_16}
\end{table}

\begin{table}[!h]
 \centering
 \begin{tabular}{c|c|c|c|c}
 $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{2}*{6} & \multirow{2}*{$(1,0)$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory coupled to a holomorphic symplectic boson} & \multirow{2}*{3 (holomorphic)} \\
 &&& $\mr{Map}(\CC^3, U /\!/G)$ & \\ \hline
 \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3 (minimal)} \\
 &&& $\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, U /\!/G)$ & \\ \hline
 \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
 &&& $T^*[-1]\mr{Map}(\CC^2, U /\!/G)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(1,1)$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (holomorphic)} \\
 &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U /\!/G)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{2 (holomorphic)} \\
 &&& $\mr{Map}(\CC^2, U /\!/G)_{\mr{dR}}$ & \\ \hline
 \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (minimal)} \\
 &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U /\!/G)$  & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ (B)} & {BF Theory coupled to a symplectic boson (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $\mr{Map}(\RR^3_{\mr{dR}}, U /\!/G)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U /\!/G)_{\mr{dR}}$ & \\ \hline
  \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a hypermultiplet valued in symplectic representation $U$ (8 supercharges).}
 \label{table_of_twists_16}
\end{table}

\begin{table}[!h]
 \centering
 \begin{tabular}{c|>{\centering}m{5ex}|c|>{\centering}m{65ex}|c}
 $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{2}*{4} & \multirow{2}*{$1$} & \multirow{2}{*}{Rank $(1,0)$} & Holomorphic BF Theory coupled to $R$-matter & \multirow{2}*{2 (holomorphic)} \\
 &&& $T^*[-1]\mr{Map}(\CC^2, R/G)$ & \\ \hline
 \multirow{2}*{3} & \multirow{2}*{$2$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to $R$-matter} & \multirow{2}*{2 (minimal)} \\
 &&&  $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/G)$ & \\ \hline
  \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a chiral multiplet valued in representation $R$ (4 supercharges).}
 \label{table_of_twists_16}
\end{table}
